Proceedings of the OHBM Hackathon 2023

### 2024-12-18 manuscript/main.tex
enh: add images and refs

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{natbib}
\usepackage[table,xcdraw]{xcolor}
\usepackage{hyperref}

@@

\include{authors}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.2\textwidth]{images/demographics.png}
    \label{fig:demographics}
    \caption{
        The four panels illustrate key demographic and participation trends for the OHBM BrainHack 2023 participants.
        \textbf{Panel A} shows the geographic distribution, with Canada, the United States, and France as the most represented countries among 13 in total.
        \textbf{Panel B} presents the career status distribution, with Early Career Researchers (ECRs)—including PhD students and postdoctoral researchers—making up half of the attendees, followed by established faculty (31.2\%) and Master's students (12.5\%).
        \textbf{Panel C} depicts participant satisfaction ratings for sessions such as Unconference, TrainTrack, and HackTrack, showing higher satisfaction for HackTrack sessions overall.
        \textbf{Panel D} examines format preferences (hybrid vs. onsite), with a stronger preference for hybrid participation among ECRs and attendees with more prior experience at BrainHack events, while onsite preference was higher among established faculty.
    }
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.2\textwidth]{images/placeholder.png}
    \label{fig:buddy-system}
    \caption{
        (a) Front, and (b) back of a buddy card.
        Buddy cards were distributed amongst all attendees who expressed interest in participating in the refined dynamic buddy system.
        Individualized who participated were asked to share their cards with other brainhackers during lunch and coffee breaks.
        The cards acted as catalist to start a conversation and exchange thoughts, experiences, and contact information.
    }
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{images/clinica-1.png}
    \label{fig:clinica-1}
    \caption{
        Scatterplot of HD BET Dice probability and correlation ratio between reference and moving images. Red color means both metrics are below the threshold, blue or purple means one of the metrics is below the threshold, green means both metrics are above the threshold.
    }
\end{figure}

@@

The joint efforts of these initiatives have established a robust foundation for cultivating a culture of collaboration and accountability within the neuroimaging community. Nonetheless, amidst these advancements, a crucial inquiry arises: What about the visual representations —the very tools through which we observe and make sense of neuroimaging results? It is within this context that we introduce Cerebro \cite{sina_mansour_l_2023_8238773}, a new Python-based software designed to create publication-quality brain visualizations (see Fig.x). Cerebro represents the next step in the quest for openness and reproducibility, where authors can share not only their code and data but also their publication figures alongside the precise scripts used to generate them. In doing so, Cerebro empowers researchers to make their visualizations fully reproducible, bridging the crucial gap between data, analysis, and representation.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.2\textwidth]{images/placeholder.png}
    \label{fig:cerebro}
    \caption{
        Cerebro – A Python-Based 3D Brain Visualization Tool. (a) Cerebro leverages an extensive array of open-source Python tools, forming a robust foundation for its functionality. It also integrates with these tools to enable seamless Pythonic neuroimaging visualizations. (b) Cerebro prioritizes principles of scriptability, reproducibility, visualization quality, cross-compatibility, and integration in its pursuit of providing a reliable solution for the neuroimaging community. (c) An illustrative Cerebro-generated visualization, accompanied by a scannable QR code linked to the publicly accessible reproduction scripts.
    }
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.2\textwidth]{images/placeholder.png}
    \label{fig:kparticles}
    \caption{
        Our compilation of k-space animations generated during the brainhack can be seen at \href{https://youtu.be/XS0LEQExGU8?si=I5Zufp3AcCbdhYIR}{YouTube}.
    }
\end{figure}

@@

One of the most memorable and engaging events at the OHBM Brainhack 2023 was the 'Rhyming Battle.'
Held before the project presentations, this unique event featured three participants who artistically expressed their experiences and challenges encountered during the hackathon.
They crafted short poems about their projects and the various aspects they faced during Brainhack, bringing a touch of lighthearted humour to their scientific endeavours \textcolor{red}{(see Appendix)}.
The Rhyming Battle provided an entertaining break from the Hackathon's more scientific aspects.
It allowed attendees to resonate with each other's experiences, celebrating the struggles and triumphs inherent in scientific projects.
The event showcased the creative and vibrant spirit of the Brainhack community.
Voting for the winner was not straightforward, as the attendees were equally good.
The prize was a single 3D homemade sculpture representing the Brainhack 2023 logo, made for the winner of the battle \textcolor{red}{(Figure x)}.
However, the enthusiasm of the battlers and the public was overwhelming, and we decided to 3D print the same sculpture for every battle participant.
Ultimately, the spirit of Brainhack community prevailed \cite{gau2021brainhack,levitis2021centering}, and every participant was celebrated as a winner.

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{natbib}
\usepackage[table,xcdraw]{xcolor}
\usepackage{hyperref}

@@

\include{authors}
\include{affiliations}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.99\textwidth]{images/demographics.png}
    \label{fig:demographics}
    \caption{
        The four panels illustrate key demographic and participation trends for the OHBM BrainHack 2023 participants.
        \textbf{Panel A} shows the geographic distribution, with Canada, the United States, and France as the most represented countries among 13 in total.
        \textbf{Panel B} presents the career status distribution, with Early Career Researchers (ECRs)—including PhD students and postdoctoral researchers—making up half of the attendees, followed by established faculty (31.2\%) and Master's students (12.5\%).
        \textbf{Panel C} depicts participant satisfaction ratings for sessions such as Unconference, TrainTrack, and HackTrack, showing higher satisfaction for HackTrack sessions overall.
        \textbf{Panel D} examines format preferences (hybrid vs. onsite), with a stronger preference for hybrid participation among ECRs and attendees with more prior experience at BrainHack events, while onsite preference was higher among established faculty.
    }
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.99\textwidth]{images/buddy-system.png}
    \label{fig:buddy-system}
    \caption{
        (a) Front, and (b) back of a buddy card.
        Buddy cards were distributed amongst all attendees who expressed interest in participating in the refined dynamic buddy system.
        Individualized who participated were asked to share their cards with other brainhackers during lunch and coffee breaks.
        The cards acted as catalist to start a conversation and exchange thoughts, experiences, and contact information.
    }
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{images/clinica.png}
    \label{fig:clinica}
    \caption{
        Scatterplot of HD BET Dice probability and correlation ratio between reference and moving images. Red color means both metrics are below the threshold, blue or purple means one of the metrics is below the threshold, green means both metrics are above the threshold.
    }
\end{figure}

@@

The joint efforts of these initiatives have established a robust foundation for cultivating a culture of collaboration and accountability within the neuroimaging community. Nonetheless, amidst these advancements, a crucial inquiry arises: What about the visual representations —the very tools through which we observe and make sense of neuroimaging results? It is within this context that we introduce Cerebro \cite{sina_mansour_l_2023_8238773}, a new Python-based software designed to create publication-quality brain visualizations (see Figure \ref{fig:cerebro}). Cerebro represents the next step in the quest for openness and reproducibility, where authors can share not only their code and data but also their publication figures alongside the precise scripts used to generate them. In doing so, Cerebro empowers researchers to make their visualizations fully reproducible, bridging the crucial gap between data, analysis, and representation.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{images/cerebro.png}
    \label{fig:cerebro}
    \caption{
        Cerebro – A Python-Based 3D Brain Visualization Tool. (a) Cerebro leverages an extensive array of open-source Python tools, forming a robust foundation for its functionality. It also integrates with these tools to enable seamless Pythonic neuroimaging visualizations. (b) Cerebro prioritizes principles of scriptability, reproducibility, visualization quality, cross-compatibility, and integration in its pursuit of providing a reliable solution for the neuroimaging community. (c) An illustrative Cerebro-generated visualization, accompanied by a scannable QR code linked to the publicly accessible reproduction scripts.
    }
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\textwidth]{images/k-particles.png}
    \label{fig:kparticles}
    \caption{
        Our compilation of k-space animations generated during the brainhack can be seen at \href{https://youtu.be/XS0LEQExGU8?si=I5Zufp3AcCbdhYIR}{YouTube}.
    }
\end{figure}

@@

One of the most memorable and engaging events at the OHBM Brainhack 2023 was the 'Rhyming Battle.'
Held before the project presentations, this unique event featured three participants who artistically expressed their experiences and challenges encountered during the hackathon.
They crafted short poems about their projects and the various aspects they faced during Brainhack, bringing a touch of lighthearted humour to their scientific endeavours (see Appendix for lyrics).
The Rhyming Battle provided an entertaining break from the Hackathon's more scientific aspects.
It allowed attendees to resonate with each other's experiences, celebrating the struggles and triumphs inherent in scientific projects.
The event showcased the creative and vibrant spirit of the Brainhack community.
Voting for the winner was not straightforward, as the attendees were equally good.
The prize was a single 3D homemade sculpture representing the Brainhack 2023 logo, made for the winner of the battle (Figure \ref{fig:skull}).
However, the enthusiasm of the battlers and the public was overwhelming, and we decided to 3D print the same sculpture for every battle participant.
Ultimately, the spirit of Brainhack community prevailed \cite{gau2021brainhack,levitis2021centering}, and every participant was celebrated as a winner.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\textwidth]{images/skull.png}
    \label{fig:skull}
    \caption{
        Skull sculpture generated using MidJourney's generative models for the main website and 3D printed replica for the Rhyming Battle winner. 
    }
\end{figure}
